---
output:
  github_document:
    html_preview: false
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# LUCIDus

<!-- badges: start -->
<!-- badges: end -->

LUCIDus implements **LUCID** (Latent Unknown Clusters by Integrating
multi-omics Data): a model that finds latent subgroups of subjects that are
simultaneously predictable from a set of exposures, characterized by
distinct multi-omics profiles, and associated with a health outcome. It
supports three integration strategies -- **early**, **parallel**, and
**serial** -- along with feature selection, missing-data handling,
prediction, g-computation, and bootstrap inference.

## Installation

```r
# install.packages("devtools")
devtools::install_github("USCbiostats/LUCIDus")
```

## A minimal example: parallel integration on the bundled HELIX data

This walks through fitting a LUCID **parallel** model -- one latent cluster
variable per omics layer, fit jointly -- on `simulated_HELIX_data`, the
simulated HELIX-study dataset bundled with the package. Parallel integration
is the right choice here because the omics data comes as three genuinely
distinct layers (methylome, transcriptome, miRNA); rather than pooling them
into one matrix, each layer gets its own cluster variable, estimated
together. For a much more detailed, narrated walkthrough of all three
architectures (including the two-step screen-then-refit workflow for real
feature selection), see `vignette("lucid_3models_normal_outcome")`.

```{r fit, warning = FALSE}
library(LUCIDus)

# The bundled HELIX dataset: one exposure (postnatal mercury exposure),
# three omics layers, two covariates, and one outcome (a liver enzyme).
data(simulated_HELIX_data)
d <- simulated_HELIX_data

G <- as.matrix(d$phenotype$hs_hg_m_scaled)
colnames(G) <- "mercury_exposure"

Z <- list(
  methylome     = d$methylome,
  transcriptome = d$transcriptome,
  miRNA         = d$miRNA
)

Co <- data.frame(
  age = d$phenotype$hs_child_age_yrs_None,
  sex = as.numeric(d$phenotype$e3_sex_None == "male")
)

Y <- as.matrix(d$phenotype$ck18_scaled)
colnames(Y) <- "ck18"

fit <- estimate_lucid(
  G = G, Z = Z, Y = Y, CoG = Co, CoY = Co,
  lucid_model = "parallel",
  family = "normal",
  K = c(2, 2, 2),
  seed = 2026
)

class(fit)
```

`lucid_model = "parallel"` selects the architecture; `K = c(2, 2, 2)` asks
for 2 clusters in each of the three layers (in `Z`'s order). `CoG`/`CoY` are
covariates adjusted for in the exposure-to-cluster and cluster-to-outcome
models respectively -- here, the same age/sex covariates for both.

### Reading the fitted model

```{r summary}
summary(fit)
```

`summary()` reports, per layer: the model specification, the exposure's
effect on cluster membership (as a log-odds/odds ratio), and each cluster's
mean omics profile. Two extractor functions read the same information
programmatically, auto-detecting that `fit` is a parallel model with no
further input:

```{r extractors}
# Each subject's hard cluster assignment, one vector per layer.
str(get_cluster_assignment(fit))

# The 5 omics features that most separate the clusters, one layer's worth.
get_top_omics_features(fit, top_n = 5)[["methylome"]]
```

### Visualizing the clusters' omics profiles

`plot_cluster_omic_profile()` shows which omics features distinguish the
clusters, and in which direction -- one figure per layer for a parallel fit:

```{r profile, fig.width = 6.5, fig.height = 4.5}
plot_cluster_omic_profile(fit, top_n = 8)[["methylome"]]
```

## Learn more

Once installed, every vignette below is available with `vignette("<name>")`.
Rendered copies are also in [`docs/`](docs/) in this repository, viewable
directly in a browser without installing the package:

- [`lucid_3models_normal_outcome`](https://htmlpreview.github.io/?https://github.com/ContiLab-usc/LUCIDus-3.0/blob/main/docs/lucid_3models_normal_outcome.html) --
  a full early/parallel/serial walkthrough, including feature selection and
  bootstrap inference, for a **continuous** outcome.
- [`lucid_3models_binary_outcome`](https://htmlpreview.github.io/?https://github.com/ContiLab-usc/LUCIDus-3.0/blob/main/docs/lucid_3models_binary_outcome.html) --
  the same walkthrough for a **binary** outcome.
- [`lucidus_full_functionality_guide`](https://htmlpreview.github.io/?https://github.com/ContiLab-usc/LUCIDus-3.0/blob/main/docs/lucidus_full_functionality_guide.html) --
  a breadth-first tour of every exported function.
- `NEWS.md` -- what changed in the current release.
