---
title: "Reproducing the R Journal paper examples with LUCIDus 3.1.0"
output:
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
params:
  full_grid: TRUE
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  error = TRUE,      # a failing example prints its condition and the knit continues
  message = FALSE,
  warning = FALSE,
  collapse = FALSE,
  comment = "#>"
)
```

## Purpose

This document runs **every code example** from

> Zhao Y, Jia Q, Goodrich JA, Conti DV (2024).
> *LUCIDus: An R Package For Implementing Latent Unknown Clustering By
> Integrating Multi-omics Data (LUCID) With Phenotypic Traits.*
> The R Journal 16/2, 4–26. (RJ-2024-012)

against the current package, to confirm that all of them still run.

**Numeric results are not expected to match the paper.** Version 3.1.0 corrects
several values that earlier versions reported incorrectly — including the
log-likelihood, the BIC, and the coding of the outcome coefficients. Wherever
output legitimately differs, a short note explains why and points at the
corresponding `NEWS.md` entry. Two of the paper's examples (`fit10` and `fit12`)
did not run at all before 3.1.0.

Every chunk is set with `error = TRUE`, so a failure is displayed and the knit
carries on rather than hiding the remaining examples. A status table at the end
lists the outcome of each one.

### Requirements

```{r requirements}
required_version <- "3.1.0"
suppressPackageStartupMessages(library(LUCIDus))
installed <- as.character(utils::packageVersion("LUCIDus"))
cat("LUCIDus version loaded:", installed, "\n")
if (utils::compareVersion(installed, required_version) < 0) {
  warning(
    "This document targets LUCIDus >= ", required_version, " but version ",
    installed, " is loaded.\n",
    "Several examples below (fit10, fit12) abort on earlier versions.\n",
    "Install the corrected package first, e.g.:\n",
    "  R CMD INSTALL /Users/qiranjia19961112/Desktop/LUCIDus-3.0"
  )
}
```

`ggplot2` is needed for the BIC figure in Section 3.3 and `visdat` for the
missingness plots in Section 3.6. Note that the paper calls `ggplot()` without
ever loading **ggplot2**; that is added here.

```{r libs}
library(ggplot2)   # not loaded in the paper, but required by its BIC figure
library(visdat)
```

### Run configuration

The paper's heaviest calls tune a 41-value penalty grid, run graphical lasso on
210 features, and draw 200 bootstrap replicates each. With `full_grid: TRUE`
(the default) the arguments below are **exactly** those printed in the paper.
Set `full_grid: FALSE` in the YAML header to re-knit quickly with coarser grids.

```{r config}
K_GRID     <- if (params$full_grid) 2:6                     else 2:4
RHO_G      <- if (params$full_grid) seq(0, 0.4, by = 0.01)  else c(0, 0.1, 0.2)
RHO_ZMU    <- if (params$full_grid) 5:10                    else c(5, 10)
RHO_ZCOV   <- if (params$full_grid) seq(0.1, 0.4, by = 0.1) else c(0.1, 0.4)
N_NOISE_HI <- if (params$full_grid) 200                     else 40
BOOT_R     <- if (params$full_grid) 200                     else 25

data.frame(
  argument   = c("K (fit8/tune_K)", "Rho_G (fit10)", "Rho_Z_Mu (fit11)",
                 "Rho_Z_Cov (fit11)", "noise features (fit13)", "R (boot1/boot2)"),
  paper      = c("2:6", "seq(0, 0.4, by = 0.01)", "5:10",
                 "seq(0.1, 0.4, by = 0.1)", "200", "200"),
  this_run   = c(deparse(K_GRID), sprintf("%d values, %g..%g", length(RHO_G),
                 min(RHO_G), max(RHO_G)), deparse(RHO_ZMU),
                 sprintf("%d values", length(RHO_ZCOV)), N_NOISE_HI, BOOT_R)
)
```

```{r registry, include = FALSE}
# Status registry.  Kept out of the displayed code so every example below stays
# verbatim; the hidden chunks after each example record whether it ran.
.reg <- new.env(parent = emptyenv())
.reg$rows <- list()

check_obj <- function(name, expected_class = NULL, section = "") {
  ok  <- exists(name, envir = globalenv(), inherits = FALSE)
  cls <- if (ok) class(get(name, envir = globalenv()))[1] else NA_character_
  status <- if (!ok) {
    "ERRORED"
  } else if (!is.null(expected_class) &&
             !inherits(get(name, envir = globalenv()), expected_class)) {
    "ran (unexpected class)"
  } else {
    "ran"
  }
  .reg$rows[[length(.reg$rows) + 1L]] <- data.frame(
    section = section, example = name,
    expected = if (is.null(expected_class)) "-" else expected_class,
    got = cls, status = status, stringsAsFactors = FALSE
  )
  invisible(NULL)
}

check_expr <- function(label, expr, section = "") {
  res <- try(force(expr), silent = TRUE)
  .reg$rows[[length(.reg$rows) + 1L]] <- data.frame(
    section = section, example = label, expected = "call", got = "-",
    status = if (inherits(res, "try-error")) "ERRORED" else "ran",
    stringsAsFactors = FALSE
  )
  invisible(NULL)
}

.t0 <- Sys.time()
```

---

# 3.1 Fitting a LUCID model

## Loading and organising the data

```{r data}
library(LUCIDus)
# load data
data("simulated_HELIX_data")
simulated_data <- simulated_HELIX_data
exposome <- as.matrix(simulated_data[["phenotype"]]$hs_hg_m_scaled)
colnames(exposome) <- "hs_hg_m_scaled"
methylomics <- simulated_data$methylome
ck18 <- as.matrix(simulated_data[["phenotype"]]$ck18_scaled)
colnames(ck18) <- "ck18_scaled"
ck18_cat <- ifelse(ck18 > mean(ck18), 1, 0)
covars <- c("hs_child_age_yrs_None","e3_sex_None")
covs <- simulated_data[["phenotype"]][covars]
covs$e3_sex_None <- ifelse(covs$e3_sex_None == "male", 1, 0)
```

## `fit1`, `fit2` — continuous and binary outcomes

```{r fit1-fit2}
# Fit a LUCID model with a continuous outcome
fit1 <- lucid(G = exposome, Z = methylomics, Y = ck18, init_omic.data.model = NULL,
              lucid_model = "early", family = "normal", K = 2)
# MLE of the LUCID model
# fit1$res_Beta
# fit1$res_Mu
# fit1$res_Sigma
# fit1$res_Gamma
# IPs of the sample
# fit1$inclusion.p
# Fit LUCID model with a binary outcome
fit2 <- lucid(G = exposome, Z = methylomics, Y = ck18_cat, init_omic.data.model = NULL,
              lucid_model = "early", family = "binary", K = 2)
```

A note beyond the paper text -- `fit1` is a plain R list, and every field on
it is documented on `?estimate_lucid`'s `@return`:

```{r fit1-object-structure}
names(fit1)
```

```{r chk1, include = FALSE}
check_obj("fit1", "early_lucid", "3.1 fitting")
check_obj("fit2", "early_lucid", "3.1 fitting")
```

## `fit3.1`, `fit3.2`, `fit4` — initialisation

```{r fit3-fit4}
# Fit LUCID model with spherical shape, equal volume
fit3.1 <- lucid(G = exposome, Z = methylomics, Y = ck18,
                lucid_model = "early", family = "normal", K = 2,
                init_par = "mclust", init_omic.data.model = "EII")
# Fit LUCID model with random guess
fit3.2 <- lucid(G = exposome, Z = methylomics, Y = ck18,
                lucid_model = "early", family = "normal", K = 2,
                init_par = "random")
# Fit LUCID model with ellipsoidal shape, varying volume, shape, and orientation
fit4 <- lucid(G = exposome, Z = methylomics, Y = ck18,
              lucid_model = "early", family = "normal", K = 2,
              init_omic.data.model = "VVV")
```

```{r chk2, include = FALSE}
check_obj("fit3.1", "early_lucid", "3.1 initialisation")
check_obj("fit3.2", "early_lucid", "3.1 initialisation")
check_obj("fit4", "early_lucid", "3.1 initialisation")
```

## `fit5` — unsupervised LUCID

```{r fit5}
# Fit an unsupervised LUCID model
fit5 <- lucid(G = exposome, Z = methylomics, Y = ck18, lucid_model = "early",
              family = "normal", K = 2, useY = FALSE)
```

```{r chk3, include = FALSE}
check_obj("fit5", "early_lucid", "3.1 unsupervised")
```

## `fit6`, `fit7` — adjusting for covariates

```{r fit6-fit7}
# Include covariates as G to X covariates
fit6 <- lucid(G = exposome, Z = methylomics, Y = ck18, lucid_model = "early", K = 2,
              family = "normal", CoG = covs)
# Include covariates as X to Y covariates
fit7 <- lucid(G = exposome, Z = methylomics, Y = ck18, lucid_model = "early", K = 2,
              family = "normal", CoY = covs)
```

```{r chk4, include = FALSE}
check_obj("fit6", "early_lucid", "3.1 covariates")
check_obj("fit7", "early_lucid", "3.1 covariates")
```

---

# 3.2 Interpreting LUCID

## `summary(fit1)`

> **Differs from the paper, by design.** Three things changed in 3.1.0:
>
> * The **log-likelihood** is now the observed-data log-likelihood of the fitted
>   model. Version 3.0.3 printed `-6721.801` for this fit; the correct value at
>   3.0.3's own estimates is `-6575.88`.
> * The **BIC** inherited that error, and additionally counted `K*M^2`
>   covariance parameters instead of Eq 13's `K*M(M+1)/2`.
> * The **outcome coefficients** are now genuinely reference-coded: an intercept
>   equal to cluster 1's level, plus explicit contrasts. The paper's
>   `cluster2 = 0.504` was in fact cluster 2's *own mean*, printed under a
>   `cluster1 = 0` heading as though it were a contrast. The real contrast
>   between the two clusters is about `1.044`.
>
> The omics means and the exposure odds ratio should closely match the paper.

```{r summary-fit1}
# summarize a simple lucid model with a continuous outcome
summary(fit1)
```

```{r chk5, include = FALSE}
check_expr("summary(fit1)", summary(fit1, auto_print = FALSE), "3.2 interpretation")
```

## `plot(fit1)` — Sankey diagrams

```{r plot1}
# Visualize LUCID model via a Sankey diagram
plot(fit1)
```

```{r plot2}
# Change the node color
plot(fit1, G_color = "yellow")
```

```{r plot3}
# Change the link color
plot(fit1, pos_link_color = "red", neg_link_color = "green")
```

```{r chk6, include = FALSE}
check_expr("plot(fit1)", plot(fit1), "3.2 interpretation")
check_expr("plot(fit1, G_color=)", plot(fit1, G_color = "yellow"), "3.2 interpretation")
check_expr("plot(fit1, link colors)",
           plot(fit1, pos_link_color = "red", neg_link_color = "green"),
           "3.2 interpretation")
```

---

# 3.3 Model selection and variable selection

## `fit8` — choosing K

> BIC values differ from the paper's Figure 4 for the reasons given above. The
> *selected* K should still be 2.

```{r fit8}
fit8 <- lucid(G = exposome, Z = methylomics, Y = ck18, lucid_model = "early",
              family = "normal", K = K_GRID)
# Check the optimal K
fit8$K
```

```{r chk7, include = FALSE}
check_obj("fit8", "early_lucid", "3.3 model selection")
```

## `tune_lucid()` and the BIC figure

```{r tune}
# Look into the tuning process in more detail
tune_K <- tune_lucid(G = exposome, Z = methylomics, Y = ck18, lucid_model = "early",
                     family = "normal", K = K_GRID)
fit9 <- tune_K$best_model
```

```{r bicplot, fig.width = 6, fig.height = 4}
ggplot(data = tune_K$tune_list, aes(x = K, y = BIC, label = round(BIC, 0))) +
  geom_point() +
  geom_line() +
  geom_text(hjust = -0.2)
```

```{r chk8, include = FALSE}
check_obj("tune_K", "list", "3.3 model selection")
check_obj("fit9", "early_lucid", "3.3 model selection")
```

## `fit10` — variable selection for G

> **This example did not run before 3.1.0.** When exactly one exposure survived
> selection, `lucid()` carried the tuned `Rho_G` into the post-selection refit,
> where the lasso requires at least two exposures, and the call aborted with
> `At least 2 exposure variables are needed for variable selection`. The refit
> on selected features is now unpenalised.

```{r fit10}
# Variable selection for G
# Add 10 more noise variables to the exposome
noise <- matrix(rnorm(420 * 10), nrow = 420)
exposome_noise <- cbind(exposome, noise)
fit10 <- lucid(G = exposome_noise, Z = methylomics, Y = ck18,
               lucid_model = "early", family = "normal", K = 2,
               Rho_G = RHO_G, seed = 1008)
# Summary of optimal lucid model
# summary(fit10)
```

```{r chk9, include = FALSE}
check_obj("fit10", "early_lucid", "3.3 variable selection")
```

## `fit11` — variable selection for Z

```{r fit11}
# Variable selection for Z
# add 10 more noise variables to the methylomics
methylomics_noise <- cbind(methylomics, noise)
fit11 <- lucid(G = exposome, Z = methylomics_noise, Y = ck18,
               lucid_model = "early", family = "normal", K = 2,
               Rho_Z_Mu = RHO_ZMU, Rho_Z_Cov = RHO_ZCOV, seed = 1008)
# Summary of optimal lucid model
# summary(fit11)
```

```{r chk10, include = FALSE}
check_obj("fit11", "early_lucid", "3.3 variable selection")
```

## `fit12` — joint selection for G and Z

> Also affected by the refit defect above; this example likewise did not
> complete before 3.1.0.

```{r fit12}
# Variable selection for G and Z jointly
fit12 <- lucid(G = exposome_noise, Z = methylomics_noise, Y = ck18,
               lucid_model = "early", family = "normal", K = 2,
               Rho_G = 0.01, Rho_Z_Mu = 10, Rho_Z_Cov = 0.5, seed = 123)
```

```{r chk11, include = FALSE}
check_obj("fit12", "early_lucid", "3.3 variable selection")
```

## `fit13` — high-dimensional Z

```{r fit13}
# Variable selection for Z (high number of features M)
set.seed(1008)
# Add 200 more noise features to the methylomics
noise <- matrix(rnorm(420 * N_NOISE_HI), nrow = 420)
methylomics_noise <- cbind(methylomics, noise)
fit13 <- lucid(G = exposome, Z = methylomics_noise, Y = ck18,
               family = "normal", lucid_model = "early", K = 2,
               Rho_Z_Mu = 20, Rho_Z_Cov = 0.6)
# Summary of optimal lucid model
# summary(fit13)
```

```{r chk12, include = FALSE}
check_obj("fit13", "early_lucid", "3.3 variable selection")
```

---

# 3.4 Deriving confidence intervals

> In 3.1.0 the bootstrap point estimate `t0` is taken from the model you supply
> rather than from a refit under a fresh random seed, so the `estimate` column
> below now agrees with `summary(fit1)`. Failed replicates are also counted and
> warned about instead of being silently dropped.

```{r boot}
# Bootstrap to obtain 95% CI (by default) for LUCID
set.seed(123)
boot1 <- boot_lucid(G = exposome, Z = methylomics, Y = ck18,
                    model = fit1, R = BOOT_R)
# 90% CIs
boot2 <- boot_lucid(G = exposome, Z = methylomics, Y = ck18,
                    model = fit1, R = BOOT_R, conf = 0.9)
```

The paper prints this call as `summary(fit1, boot.se = boot1))`, which has an
unbalanced closing parenthesis and is a typo in the article. Corrected here:

```{r boot-summary}
# Summary table with 95% bootstrap CIs
summary(fit1, boot.se = boot1)
```

```{r chk13, include = FALSE}
check_obj("boot1", "list", "3.4 inference")
check_obj("boot2", "list", "3.4 inference")
check_expr("summary(fit1, boot.se = boot1)",
           summary(fit1, boot.se = boot1, auto_print = FALSE), "3.4 inference")
```

---

# 3.5 Prediction

> **Now matches the paper for the first time.** The article prints
> `table(pred1$pred.x)` with labels `1` and `2`, but the shipped code returned
> `0` and `1` in both 3.0.3 and pre-fix 3.1.0. Cluster labels are now `1..K`
> throughout, consistent with Eq 21, `summary()`, and the `inclusion.p` columns.
> The counts themselves will differ from the paper's 223/197.

```{r predict}
# Predict cluster with information of Y
pred1 <- predict_lucid(model = fit1, G = exposome, Z = methylomics, Y = ck18)
# Predict cluster without information of Y
pred2 <- predict_lucid(model = fit1, G = exposome, Z = methylomics)
# Predicted cluster label
table(pred1$pred.x)
# Predicted outcome
pred1$pred.y[1:5]
```

```{r chk14, include = FALSE}
check_obj("pred1", "list", "3.5 prediction")
check_obj("pred2", "list", "3.5 prediction")
```

---

# 3.6 Incorporating missingness in multi-omics data

Two quirks in the paper's own setup are reproduced verbatim rather than
corrected, so that this section matches the article:

* `arrayInd(sample(1000, 0.1 * 1000), dim(methylomics))` draws from the first
  1000 of the 4200 cells in `methylomics`, so the realised sporadic missingness
  rate is about 2.4%, not the 10% the expression suggests.
* `methylomics_miss_listwise[sample(1:100, 30), ]` selects list-wise rows only
  from the first 100 of 420 observations.

```{r missing-setup, fig.width = 7, fig.height = 4}
library(visdat)
set.seed(1)
methylomics_miss_sporadic <- methylomics_miss_listwise <- as.matrix(methylomics)
index <- arrayInd(sample(1000, 0.1 * 1000), dim(methylomics))
methylomics_miss_sporadic[index] <- NA # sporadic missing pattern
methylomics_miss_listwise[sample(1:100, 30), ] <- NA # listwise missing pattern
vis_miss(as.data.frame(methylomics_miss_sporadic))
```

```{r missing-plot2, fig.width = 7, fig.height = 4}
vis_miss(as.data.frame(methylomics_miss_listwise))
```

```{r fit14-fit15}
fit14 <- lucid(G = exposome, Z = methylomics_miss_listwise, Y = ck18,
               lucid_model = "early", K = 2, family = "normal")
fit15 <- lucid(G = exposome, Z = methylomics_miss_sporadic, Y = ck18,
               lucid_model = "early", K = 2, family = "normal")
# summary(fit15)
```

```{r chk15, include = FALSE}
check_obj("fit14", "early_lucid", "3.6 missing data")
check_obj("fit15", "early_lucid", "3.6 missing data")
```

A check the paper does not perform — that list-wise rows are returned as `NA`
rather than filled with fabricated values, and that observed cells are never
altered:

```{r missing-invariants}
lw <- which(rowSums(is.na(methylomics_miss_listwise)) == ncol(methylomics_miss_listwise))
cat("list-wise rows still NA in fit14$Z:      ", all(is.na(fit14$Z[lw, ])), "\n")
obs <- !is.na(methylomics_miss_sporadic)
cat("observed cells unchanged in fit15$Z:     ",
    isTRUE(all.equal(fit15$Z[obs], methylomics_miss_sporadic[obs])), "\n")
cat("sporadic cells imputed and finite:       ",
    all(is.finite(fit15$Z[!obs])), "\n")
```

---

# 3.7 LUCID in Parallel

> `summary(fit)$BIC` now resolves for parallel and serial models; it was
> previously an early-model-only field that returned `NULL` elsewhere.

```{r fit16}
# Create a list of multi-omics data
omics_lst <- simulated_data[-which(names(simulated_data) == "phenotype")]
Z = omics_lst[c(1:3)]
# LUCID in parallel, adjusting for the covariates for the E-X and X-Y associations
fit16 <- lucid(G = exposome, Z = Z, Y = ck18, K = list(2, 2, 2), family = "normal",
               CoY = covs, CoG = covs,
               lucid_model = "parallel", useY = TRUE)
# print the summary of the LUCID in parallel model
summary(fit16)
```

Beyond the paper text: `fit16`'s object structure. Two fields differ from
`fit1` above -- `N` (sample size) is present here but not for early, and
`z` (the joint E-step responsibility array across layers, before it is
marginalized into `inclusion.p`) appears only for parallel.

```{r fit16-object-structure}
names(fit16)
```

```{r fit17}
# LUCID in parallel, tune for the number of clusters for methylomics
fit17 <- lucid(G = exposome, Z = Z, Y = ck18, K = list(2, 2:3, 2), family = "normal",
               lucid_model = "parallel", useY = TRUE)
# summary(fit17)
```

```{r chk16, include = FALSE}
check_obj("fit16", "lucid_parallel", "3.7 parallel")
check_obj("fit17", "lucid_parallel", "3.7 parallel")
check_expr("summary(fit16)", summary(fit16, auto_print = FALSE), "3.7 parallel")
```

---

# 3.8 LUCID in Serial

```{r fit18}
# LUCID in serial, adjusting for the covariates of the E-X and X-Y associations
# Tune the number of clusters for methylome and transcriptome
# All 3 sub-models are LUCID early integration models and each with two latent
# clusters for each layer
fit18 <- lucid(G = exposome, Z = Z, Y = ck18,
               lucid_model = "serial", CoY = covs, CoG = covs,
               K = list(2:3, 2:3, 2), useY = TRUE, family = "normal")
# Print the summary of the LUCID in serial model
summary(fit18)
```

Beyond the paper text: `fit18`'s object structure. Serial adds `submodel`
(the fitted stage models, each a complete `early_lucid`/`lucid_parallel`
object) and `res_Delta` (between-stage transition coefficients).
`likelihood` and `select` are present, same as early/parallel, but are
aggregates over stages: `likelihood` sums each stage's own log-likelihood
(a serial chain has no single joint EM loop to report one from), and
`select` is stage 1's own selection only -- the one stage whose `G` is the
cohort's real exposures, not a previous stage's cluster probabilities.

```{r fit18-object-structure}
names(fit18)
cat("top-level likelihood (sum over stages):", fit18$likelihood, "\n")
cat("top-level select is stage 1's select:",
    identical(fit18$select, fit18$submodel[[1]]$select), "\n")
```

```{r fit19}
# LUCID in serial with the first sub-model being LUCID in parallel
# and the second sub-model being LUCID early integration
# Rearrange the omics list to match the new structure of the LUCID in serial model
Z_new = list(list(omics_lst$methylome, omics_lst$transcriptome), omics_lst$miRNA)
# Fit the LUCID in serial model with the new omics list and the new K list
fit19 <- lucid(G = exposome, Z = Z_new, Y = ck18,
               lucid_model = "serial", CoY = covs, CoG = covs,
               K = list(list(2, 2), 2), useY = TRUE, family = "normal")
# summary(fit19)
```

```{r chk17, include = FALSE}
check_obj("fit18", "lucid_serial", "3.8 serial")
check_obj("fit19", "lucid_serial", "3.8 serial")
check_expr("summary(fit18)", summary(fit18, auto_print = FALSE), "3.8 serial")
```

---

# Status of every example

```{r status, echo = FALSE}
status <- do.call(rbind, .reg$rows)
knitr::kable(status, row.names = FALSE)
```

```{r status-summary, echo = FALSE}
n_ok  <- sum(status$status == "ran")
n_bad <- sum(status$status != "ran")
cat(sprintf("%d of %d examples ran; %d errored.\n", n_ok, nrow(status), n_bad))
if (n_bad > 0) {
  cat("\nExamples that did not run:\n")
  print(status[status$status != "ran", c("section", "example", "status")],
        row.names = FALSE)
}
cat(sprintf("\nTotal knit time: %.1f minutes (full_grid = %s)\n",
            as.numeric(difftime(Sys.time(), .t0, units = "mins")),
            params$full_grid))
```

# Spot checks against known-correct values

Invariants established independently of the paper (see `NEWS.md`):

```{r spotchecks, echo = FALSE}
chk <- function(label, value, expected, tol = NA) {
  ok <- if (is.na(tol)) isTRUE(all.equal(value, expected))
        else isTRUE(abs(value - expected) < tol)
  data.frame(check = label, observed = format(value), expected = format(expected),
             ok = ok, stringsAsFactors = FALSE)
}
s1 <- summary(fit1, auto_print = FALSE)
rows <- list(
  chk("fit1 log-likelihood", round(fit1$likelihood, 2), -6575.89, tol = 0.5),
  chk("fit1 number of parameters", s1$model_fit$n_parameters, 136),
  chk("fit8 selected K", fit8$K, 2L),
  chk("pred.x labels are 1..K", paste(sort(unique(pred1$pred.x)), collapse = ","), "1,2"),
  chk("fit1 converged", fit1$em_control$converged, TRUE)
)
knitr::kable(do.call(rbind, rows), row.names = FALSE)
```

# Session information

```{r session, echo = FALSE}
sessionInfo()
```
